Word2vec learns effective distance of scientific co-affiliation

### 2020-01-27 paper/current/main.tex
Supp figure for absolute and proportion publications over time

\subsection*{Data}
%% Main dataset
% Do we need to add the Leiden field classificaiton infomration? It doesn't seem like its relevant for the current analysis.
% Do we need to talk about how we define mobility in relation to past papers?
We source co-affiliation trajectories of authors from the Web of Science database hosted by the Center for Science and Technology Studies at Leiden University. 
Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\cite{caron2014disambiguation} and when performance is strongest (ref to SI?). 
This yields 37,542,144 author-affiliation representing 12,963,792 authors. 
Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year. 
Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
Mobile authors constitute 3,709,869 or 28.6 percent of all authors, and 22,436,637 author-affiliation combinations.

@@

\newpage
\section{Supporting Information}
\beginsupplement

%
% Figure - reverse CDF by scale
%
\begin{figure}[hp!]
	\centering
	\label{fig:supp:rcdf_by_scale}
	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
	\caption{
		\textbf{Reverse cumulative-distribution function of mobile authors by geographic scale.}
		\textbf{a.}
		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data. 
		\textbf{b.} 68 percent of mobile authors have at least two cities represented in their career trajectories.
		\textbf{c.} 45 percent of mobile authors have 2 or more regions represented in their career trajectories.
		\textbf{d.} Only 14 percent of mobile authors had 2 or more countries represented in their career trajectories. 
	}
\end{figure}

\newpage
%
% Figure - gravity correlation
%
\begin{figure}[hp!]
	\centering
	\label{fig:supp:gravity_correlation}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding proximity explains more variance for global, within, and between country flux than geographic distance.}
		\textbf{a.}
		Embedding proximity (cosine similarity between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
		\textbf{c-d.}	embedding proximity explains more variance when considering only pairs of organizations within the same country. 
		\textbf{e-f.} embedding proximity more robust than geographic distance for pairs of organizations in different countries. 
	}
\end{figure}

\newpage
\printbibliography{}

>>>>

\subsection*{Data}
%% Main dataset
% Do we need to add the Leiden field classificaiton infomration? It doesn't seem like its relevant for the current analysis.
% Do we need to talk about how we define mobility in relation to past papers?
We source co-affiliation trajectories of authors from the Web of Science database hosted by the Center for Science and Technology Studies at Leiden University. 
Trajectories are constructed from author affiliations listed on the byline of publications for a given author.
Given the limitations of author-name disambiguation, we limit to papers published after 2008, when the Web of Science began providing full names and institutional affiliations~\cite{caron2014disambiguation} and when performance is strongest (ref to SI?). 
This yields 37,542,144 author-affiliation representing 12,963,792 authors. 
Each author-affiliation combination is associated with the publication year and a unique id that maps the affiliation to a disambiguate organization. 
Combinations are also associated with a publication-level disciplinary classification, one of ``Social sciences and humanities'',
``Biomedical and health sciences'', ``Physical sciences and engineering'', ``Life and earth sciences'', and ``Mathematics and computer science''.
Trajectories are represented as the list of author-affiliation combinations, ordered by year of publication, and randomly ordered for combinations within the same year. 
Authors are classified as mobile when they have at least two distinct organization ids in their trajectory, meaning that they have published using two or more distinct affiliations between 2008 and 2019.
Mobile authors constitute 3,709,869 or 28.6 percent of all authors, and 22,436,637 author-affiliation combinations.

@@

\newpage
\beginsupplement
\section{Supporting Information}

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:pubs_over_time}
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
		There is no evidence of major changes in publication patterns of mobile authors during this time period. 
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased. 
		\textbf{c.} 
		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time. 
		\textbf{d.} 
		The proportion of authors publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion. 
		However, the proportion of Social Science and Humanities publications has been steadily increasing. 
	}
\end{figure}

\newpage
%
% Figure - reverse CDF by scale
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:rcdf_by_scale}
	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
	\caption{
		\textbf{Reverse cumulative-distribution function of mobile authors by geographic scale.}
		\textbf{a.}
		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data. 
		\textbf{b.} 68 percent of mobile authors have at least two cities represented in their career trajectories.
		\textbf{c.} 45 percent of mobile authors have 2 or more regions represented in their career trajectories.
		\textbf{d.} Only 14 percent of mobile authors had 2 or more countries represented in their career trajectories. 
	}
\end{figure}

\newpage
%
% Figure - gravity correlation
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:gravity_correlation}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding proximity explains more variance for global, within, and between country flux than geographic distance.}
		\textbf{a.}
		Embedding proximity (cosine similarity between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
		\textbf{c-d.}	embedding proximity explains more variance when considering only pairs of organizations within the same country. 
		\textbf{e-f.} embedding proximity more robust than geographic distance for pairs of organizations in different countries. 
	}
\end{figure}

\clearpage
\printbibliography{}
